---
title: "Hw 2/23"
author: "Runan Yao"
date: "February 23, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=5) 
library('gtools') # used for dirichlet r.v. generate
```

# Basic Function
## Genderate X

We are getting a X every time

```{r}
getX <- function(mean, sigma)
{
  return(rmultinom(1, mean, sigma))
}

```

## Calculate distribution of theta

Since theta is following Dirichlet Distribution, the marginal distribution of theta i is following a beta distribution. 

```{r}

#calcConstant <- function(alpha){
#  return(exp(sum(lgamma(alpha)) - lgamma(sum(alpha))))
#}

calMarginalAlpha <- function(X, i){
  X.dim = length(X[,1])
  alpha <- rowSums(X)  
  #balpha = calcConstant(alpha)
  return(c(alpha[i], sum(alpha) - alpha[i]))
}

calcDensity <- function( alpha )
{
  x <- seq(0,1,length = 200)
  return(dbeta(x, alpha[1], alpha[2]))
}
```

## Plot function

```{r}
plotCurrent <- function( data, n )
{
  par(mfrow = c(1,3))
  thetaValue <- seq(0,1, length = 200)
  length(data[1])
  plot(x = thetaValue, y = data[,1], type='l',  main= paste("Theta 1 in run ", n ))
  plot(x = thetaValue, y = data[,2], type='l',  main= paste("Theta 2 in run ", n ))
  plot(x = thetaValue, y = data[,3], type='l',  main= paste("Theta 3 in run ", n ))
}
```

## other supporting function

```{r}
calcMean <- function( DensityData )
{
  thetaValue <- seq(0,1, length = 200)
  return(sum(DensityData * thetaValue / sum(DensityData)))
}

calcVar <- function( DensityData )
{
  mean <- calcMean(DensityData)
  thetaValue <- seq(0,1, length = 200)
  return(sum(DensityData*(thetaValue - mean)^2))
}

calcDensityAndPlot <- function(Data, i)
{
    alpha_1 <- calMarginalAlpha(Data, 1)
    alpha_2 <- calMarginalAlpha(Data, 2)
    alpha_3 <- calMarginalAlpha(Data, 3)
    
    DensityData_1 <- calcDensity(alpha_1)
    DensityData_2 <- calcDensity(alpha_2)
    DensityData_3 <- calcDensity(alpha_3)

    plotCurrent(cbind(DensityData_1,DensityData_2,DensityData_3), i)
}

calcDensityAndPrintMeanSn <- function(Data)
{
    alpha_1 <- calMarginalAlpha(Data, 1)
    alpha_2 <- calMarginalAlpha(Data, 2)
    alpha_3 <- calMarginalAlpha(Data, 3)
    
    DensityData_1 <- calcDensity(alpha_1)
    DensityData_2 <- calcDensity(alpha_2)
    DensityData_3 <- calcDensity(alpha_3)
  
      print(calcMean(DensityData_1))
      print(calcVar(DensityData_1)/10000)
      print(calcMean(DensityData_2))
      print(calcVar(DensityData_2)/10000)
      print(calcMean(DensityData_3))
      print(calcVar(DensityData_3)/10000)
}

```

# Start Simulation

## Start with theta ~ Dir(1)
```{r}
D <- numeric(length=3)
D <- matrix(D, nrow = 3, ncol = 1)
D[1,1] = 1

calcDensityAndPlot(D, 0)

```

## Sample X1 and plot the marginal distribution
```{r}
mean = 1
sigma = c(0.5, 0.35, 0.15)
Data <- 0
t = 1

for(i in seq(1, 50000))
{
  X <- getX(mean, sigma)
  if(i == 1)
  {
    Data = X
  }
  else
  {
    Data <- cbind(Data,X)
  }
  
  if(i %% t == 0)
  {
    t = t*2
    calcDensityAndPlot(Data, i)
  }
  
}

calcDensityAndPlot(Data, 50000)
```

## Calculate Mean and Sn

```{r}
calcDensityAndPrintMeanSn(Data)
```

# Conclusion

By simulation, we find the marginal posterior distribution of thetas. 

It is a normal distribution, which is following Central Limit Theorem.
